Lipid Interactome Monthly Invoice

### 2025-11-28 HourlyTracking/202509_GG-Hours.qmd
Pushing latest formatting edit of manuscript

---
title: Lipid Interactome Monthly Invoice
subtitle: Invoice Number 20250801
author: "Gaelen Guzman"
date: "2025 09 04"
output: 
  pdf_document:
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
header-includes:
  - "\\usepackage{fancyhdr}"
  - "\\pagestyle{fancy}"
  - "\\fancyhead[L]{Gaelen Guzman}"
  - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
  - "\\fancyhead[R]{2025 09 04}"
  - "\\fancyhead[R]{Invoice Number 20250801}"
  - "\\fancyfoot{}"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "\\renewcommand{\\footrulewidth}{0pt}"
---

@@

Please find below the hours I logged for the month of August 2025, with descriptions of each day's activity. In total, I performed 5 hours of work at an hourly rate of $50 (USD), for a total bill of $250.

@@

# Read the Hours.csv file and handle unnamed columns
hours_data <- read_csv(here("HourlyTracking/hours.csv"), col_names = c("Date", "Hours", "Activity"), show_col_types = FALSE) |>
  mutate(Date = as.Date(as.character(Date), format = "%Y%m%d")) |>
  select(Date, Hours, Activity) |>
  filter(Date >= as.Date("2025-08-01") & Date < as.Date("2025-09-01")) %>%  # Filter for April 2025
  glimpse()

>>>>

---
title: Lipid Interactome Monthly Invoice
subtitle: Invoice Number 20250901
author: "Gaelen Guzman"
date: "2025 10 31"
output: 
  pdf_document:
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
header-includes:
  - "\\usepackage{fancyhdr}"
  - "\\pagestyle{fancy}"
  - "\\fancyhead[L]{Gaelen Guzman}"
  - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
  - "\\fancyhead[R]{2025 09 04}"
  - "\\fancyhead[R]{Invoice Number 20250901}"
  - "\\fancyfoot{}"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "\\renewcommand{\\footrulewidth}{0pt}"
---

@@

Please find below the hours I logged for the month of September 2025, with descriptions of each day's activity. In total, I performed 5 hours of work at an hourly rate of $50 (USD), for a total bill of $250.

@@

# Read the Hours.csv file and handle unnamed columns
hours_data <- read_csv(here("HourlyTracking/hours.csv"), col_names = c("Date", "Hours", "Activity"), show_col_types = FALSE) |>
  mutate(Date = as.Date(as.character(Date), format = "%Y%m%d")) |>
  select(Date, Hours, Activity) |>
  filter(Date >= as.Date("2025-09-01") & Date < as.Date("2025-10-01")) %>%  # Filter for April 2025
  glimpse()

### 2025-11-28 HourlyTracking/202510_GG-Hours.qmd
Pushing latest formatting edit of manuscript

---
title: Lipid Interactome Monthly Invoice
subtitle: Invoice Number 20250901
author: "Gaelen Guzman"
date: "2025 10 31"
output: 
  pdf_document:
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
header-includes:
  - "\\usepackage{fancyhdr}"
  - "\\pagestyle{fancy}"
  - "\\fancyhead[L]{Gaelen Guzman}"
  - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
  - "\\fancyhead[R]{2025 09 04}"
  - "\\fancyhead[R]{Invoice Number 20250901}"
  - "\\fancyfoot{}"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "\\renewcommand{\\footrulewidth}{0pt}"
---

@@

Please find below the hours I logged for the month of September 2025, with descriptions of each day's activity. In total, I performed 5 hours of work at an hourly rate of $50 (USD), for a total bill of $250.

@@

# Read the Hours.csv file and handle unnamed columns
hours_data <- read_csv(here("HourlyTracking/hours.csv"), col_names = c("Date", "Hours", "Activity"), show_col_types = FALSE) |>
  mutate(Date = as.Date(as.character(Date), format = "%Y%m%d")) |>
  select(Date, Hours, Activity) |>
  filter(Date >= as.Date("2025-09-01") & Date < as.Date("2025-10-01")) %>%  # Filter for April 2025
  glimpse()

>>>>

---
title: Lipid Interactome Monthly Invoice
subtitle: Invoice Number 20251001
author: "Gaelen Guzman"
date: "2025 10 31"
output: 
  pdf_document:
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
header-includes:
  - "\\usepackage{fancyhdr}"
  - "\\pagestyle{fancy}"
  - "\\fancyhead[L]{Gaelen Guzman}"
  - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
  - "\\fancyhead[R]{2025 10 31}"
  - "\\fancyhead[R]{Invoice Number 20251001}"
  - "\\fancyfoot{}"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "\\renewcommand{\\footrulewidth}{0pt}"
---

@@

Please find below the hours I logged for the month of October 2025, with descriptions of each day's activity. In total, I performed 2 hours of work at an hourly rate of $50 (USD), for a total bill of $100.

@@

# Read the Hours.csv file and handle unnamed columns
hours_data <- read_csv(here("HourlyTracking/hours.csv"), col_names = c("Date", "Hours", "Activity"), show_col_types = FALSE) |>
  mutate(Date = as.Date(as.character(Date), format = "%Y%m%d")) |>
  select(Date, Hours, Activity) |>
  filter(Date >= as.Date("2025-10-01") & Date < as.Date("2025-11-01")) %>%  # Filter for April 2025
  glimpse()
